Title

### 2023-10-10 main.tex
Update main.tex

% Use "Eq" instead of "Equation" for equation citations.
% }}}
\section{Introduction} % {{{

@@

\tbnote{Entiendo que su punto es que los canales de Pauli se podrían hacer de una forma
similar pero en lugar de usar los qubits de ancilla para crear las probabilidades, crearlas
de otra forma que sea mejor y que entonces no tiene mucho sentido el artículo.  \\
La verdad no sé bien cómo contestar a este comentario. \\
Una forma podria ser cambiar un poco el enfoque. 
Hacer que el objetivo principal sea
simular un mapa dinámico (en lugar de simular canales de Pauli asi nada mas)  y estudiar como entra el parámetro en juego. 
Podemos decir que aunque en general se ha hecho mucha simulación cuántica, 
no se le ha dado mucho enfoque a operaciones parametrizadas.\\
Luego, decir que para simular mapas parametrizados de Pauli,
necesitamos empezar con un algortimo para canales y que funcione para cualquier canal de Pauli.
Al ser tan general, no es perfecto, pues varios canales se podrian hacer más fácil, 
pero lo bueno es que es un mismo algorigmo para todos, lo que 
nos va a permitir usarlo para canales parametrizados, ya que entonces sólo habrá que
mover un parámetro, en vez de cambiar todo el algoritmo para pasar de un canal a otro.\\
Luego, generalizamos el circuito para ahora sí hacerlo en mapas dinámicos y vemos qué onda con lo de 
poder reducir el número de parámetros, con lo que
llegamos al teorema de los circuitos 1PR y etc.
También corremos el circuito en computadoras cuánticas,
lo que ayuda a ver que haber modificado el circuito para que tenga un sólo parámetro
(hacer lo de meter las matrices A y B), no afectó mucho la fidelidad.
Observar cómo se afecta o no la fidelidad al hacer eso puede ser una motivación de
haber usado compus cuanticas. \\
Al final, también recalcar que el resutlado sobre 1PR es más
general que solo canales de Pauli y puede ser útil
para cualquier curcuito parametrizado.}

@@

In this section we propose a quantum circuit that simulates $N$-qubit Pauli
channels. \revnote{At this point I am missing a proper definition of a "quantum circuit" consistent with the mathematical formalism. The authors start from the very basic regarding Pauli channels, but give for granted the quantum circuit formalism.} \tbnote{Agregué algo abajo}

@@

Our systems always consists of some number of qubits,
that can be divided into the ones to which we will apply the quantum channel,
 or ``principal qubits'' and the ones that help us complete said operation, or ``ancilla qubits''.
The circuit implements a unitary operator $U$ on the 
system consisting of all the qubits 
and then the principal qubits are measured.
}

@@

Finally, using the representation of Pauli channels in a tetrahedron as in
\eref{eq: conditions-tetrahedron}, we show in \fref{Fig3} the diamond
fidelity defined by \eref{eq:diamond-fid} for the channels analyzed.  We can
see that channels close to the completely depolarizing channel (that is close
to the center of the tetrahedron) have a high $f$, while those close to unitary
channels have much lower $f$. \revnote{So another way to see this is that the simulation through the proposed decomposition works only for depolarising channels, and fails otherwise. } 
\tbnote{La respuesta a esto puede incluir lo siguiente: 
It works better for depolarizing channels, yes, but still has considerably big zone with high fidelity.}
 This is reasonable because quantum computers are
prone to errors that depolarize qubits, which isn't very problematic when
trying to simulate depolarization but it is when simulating unitary processes.
Moreover, the algorithm of \fref{Fig2} is not optimal for
unitary channels \revnote{why?} (that is, the channels corresponding to the vertices of the
tetrahedron).  These straightforward channels could be accomplished more
efficiently by simply applying the corresponding Pauli operation directly. \revnote{I wholeheartedly agree with this statement, and I would go so far as to claim that this is true in general, even at the center of the tethraedron.}
\tbnote{Este comentario se conecta con lo del 
primer comentario, que no sé bien cómo contestar.}
Nevertheless, due to its general design to accommodate any Pauli channel, the
algorithm employs numerous quantum gates even in such scenarios. \revnote{but this is a severe disadvantage, that begs the question: what is the advantage?}
\tbnote{As I see it, an advantage is that only one circuit arrengment is needed for any channel. We don't have to change
the circuit to implement different channels, only need to change parameters.
This allows us to consider parametrized circuits and then explore what happens when
we constrain to only one parametrized operation.}\\
\tbnote{Se podría entonces cambiar la ultima oración del texto por la siguiente para que quede más claro:}
{\color{green} This disadvantage comes from the fact
that the circuit is  fully general and applicable to any Pauli channel, but that means that sometimes
it is not the most straightforward algorithm to simulate a Pauli channel.
However, the main advantage is that if we want 
to simulate many Pauli channels (for example,
for simulating a Pauli dynamical map as we will see later),
we only have to change a couple of angles in the circuit and
not completely reconstruct it. 
And as we will see, sometimes only changing
one angle in the circuit will be enough.}

@@

Just as Pauli channels, Pauli dynamical maps can be implemented using the circuit
of \fref{Fig1}. However, there is one difference: 
the state to be created on the ancilla qubits now 
depends on a parameter $p$, and it is represented by the expression:
\begin{eqnarray}
\label{eq: parametrized state}
\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle.
\end{eqnarray}
Thus, we temporarily shift our focus from Pauli
channels and dynamical maps to the general problem of 
creating a circuit to generate a curve of
states like the one described in \eref{eq: parametrized state}.

@@

In this work, we found a quantum algorithm for 
simulating Pauli channels in $N$-qubit systems and
generalized it to Pauli dynamical maps
by using parametrized quantum circuits \revnote{imprecise}.
Furthermore, we implemented single-qubit Pauli channels
on one of IBM's quantum computers
and obtained their fidelities. 
Finally, when working with Pauli dynamical maps,
we searched for a way of simplifying the parametrized circuit \revnote{This reasoning I miss, simplifying for achieving what goal? }
by requiring that only one single-qubit rotation depends on the parameter.
In theorem \ref{theorem2} we found the general mathematical conditions for 
this, applicable to any parametrized circuit.

Therefore, this work presents yet another example of the current
exploration into simulating open quantum
systems in quantum computers,
and we observe the big effect that the error of quantum computers have
on these simulations. \revnote{There is no quantification of this, it´s not even the focus of the paper}
On the other hand, the result
of theorem \ref{theorem2}
shows what can be done with the condition of using only one
parametrized rotation and
can be applied to any quantum algorithm that requires parametrized circuits,
such as those used for quantum machine learning. \revnote{citation required here}

>>>>

% Use "Eq" instead of "Equation" for equation citations.
% }}}

\tbnote{Propuesta haciendo unos cambios de enfoque que menciono en la intro:}\\
$\;$ \\

{\color{green}
Pauli channels are fundamental in the context of quantum computing as they
model the simplest kind of noise in quantum devices, and
Pauli dynamical maps are parametrized Pauli channels,
which can model a continuous transformation of a quantum device.
In this article, we propose a quantum
algorithm for simulating
Pauli dynamical maps
by using a parametrized quantum circuit.
We also establish the mathematical conditions for an
$N$-qubit transformation to be achievable using a parametrized circuit where
only one single-qubit operation depends on the parameter. 
The implementation of the proposed circuit is demonstrated using IBM's quantum computers 
for the case of one qubit, and the fidelity of this implementation is reported. 
}
\section{Introduction} % {{{

@@

\tbnote{Entiendo que su punto es que los canales de Pauli se podrían hacer de una forma
similar pero en lugar de usar los qubits de ancilla para crear las probabilidades, crearlas
de otra forma que sea mejor y que entonces no tiene mucho sentido el artículo.  \\
La verdad no sé bien cómo contestar a este comentario. \\
Una forma podria ser cambiar un poco el enfoque. 
Hacer que el objetivo principal sea
simular un mapa dinámico (en lugar de simular canales de Pauli asi nada mas)  y estudiar como entra el parámetro en juego. 
Luego, decir que para simular mapas parametrizados de Pauli,
necesitamos empezar con un algortimo para canales y que funcione para cualquier canal de Pauli.
Al ser tan general, no es perfecto, pues varios canales se podrian hacer más fácil, 
pero lo bueno es que es un mismo algorigmo para todos, lo que 
nos va a permitir usarlo para canales parametrizados, ya que entonces sólo habrá que
mover un parámetro, en vez de cambiar todo el algoritmo para pasar de un canal a otro.\\
Luego, generalizamos el circuito para ahora sí hacerlo en mapas dinámicos y vemos qué onda con lo de 
poder reducir el número de parámetros, con lo que
llegamos al teorema de los circuitos 1PR y etc.
También corremos el circuito en computadoras cuánticas,
lo que ayuda a ver que haber modificado el circuito para que tenga un sólo parámetro
(hacer lo de meter las matrices A y B), no afectó mucho la fidelidad.
Observar cómo se afecta o no la fidelidad al hacer eso puede ser una motivación de
haber usado compus cuanticas. \\
Al final, también recalcar que el resutlado sobre 1PR es más
general que solo canales de Pauli y puede ser útil
para cualquier curcuito parametrizado.} \\
$\;$ \\
Ahora sí la nueva propuesta de la intro (los primeros dos párrafos son iguales): \\
$\;$ \\
{\color{green}

Since their inception, quantum computers were proposed as powerful tools for
the simulation of quantum systems~\cite{feynman1982simulating}.  Being open
quantum systems of fundamental~\cite{Zur91,RevModPhys.76.1267} and
practical~\cite{breuer2007theory} interest, there has been efforts towards the
simulation of the evolution of open quantum systems~\cite{Garcia, Wang,Weimer}
and specifically for quantum channels~\cite{Xin,Wei,Zanetti}.
Such quantum algorithms can be represented using what is known as a quantum
circuit~\cite{chuangbook}, which we will study in section \ref{sec: Circuit for a Pauli Channel}.

To represent the algorithms implemented in quantum computers, either to
simulate a physical system or for some other purpose, one often uses a quantum
circuit~\cite{chuangbook}.

However, in this article, our main goal is not to implement Pauli channels, but to study and implement Pauli dynamical maps, which are continuous parametrized curves of Pauli channels. 
These maps can be used to model continuous change of a qubit instead of only discrete jumps.
Implementing these maps will lead us to study  quantum algorithms with free parameters, 
something that is common in areas such as quantum machine learning~\cite{Benedetti}.
This can be done using parametrized quantum circuits, which consist of quantum circuits in which one or more operations depend on a free parameter. \\

Our study of such circuits for the use of simulating Pauli dynamical maps will lead 
us to theorem 2, in which we find general condition for any parametrized
transformation (for example, a Pauli dynamical map) to be achievable on a quantum circuit 
with only one single-qubit rotation dependent on the parameter.
Said parameter is in some sense a knob that we can control to continuously perform the transformation by
only having to move one number. \\

We start the article by providing the definition of quantum channels, the general framework
used here, and multi-qubit Pauli channels in section \ref{sec: Pauli Channels}.
Then, since our main objective is to obtain a parametrized circuit for Pauli dynamical maps, we will first need a 
circuit that can implement any Pauli channel by only changing some parameters
in the quantum gates and without changing the design of the circuit itself.
Therefore, in section\ref{sec: Circuit
for a Pauli Channel} we present such a circuit
and we also show its implementation using IBM's quantum computers for the particular case of single-qubit Pauli channels and some two-qubit ones.
In section \ref{sec: 1PR Circuits}, we adapt the algorithm to dynamical maps.
Then we aim to simplify the algorithm so that it only contains one parametrized single-qubit rotation, 
and in the process we contribute to the work in parametrized quantum circuits by establishing   in
\ref{theorem2} which general quantum transformations
can be implemented this way.
Finally, in
section \ref{sec: 1PR circuit for a Pauli map}, we conclude analyzing the Pauli
dynamical maps that fulfill the conditions of theorem \ref{theorem2}. 
}

@@

In this section we propose a quantum circuit that simulates $N$-qubit Pauli
channels. \revnote{At this point I am missing a proper definition of a "quantum circuit" consistent with the mathematical formalism. The authors start from the very basic regarding Pauli channels, but give for granted the quantum circuit formalism.} \tbnote{Agregué algo abajo:}\\

@@

Our systems always consists of some number of qubits,
that can be divided into the ones to which we will apply the quantum channel,
 or ``principal qubits'' and the ones that help us complete said operation, or ``ancilla qubits''.
The circuit implements a unitary operator $U$ on the 
system consisting of all the qubits 
and then the principal qubits are measured.

We will create a general circuit that can implement any $N$-qubit Pauli channel
by only changing some parameters and not changing the design of the circuit itself.
This is done with the intent of converting it into a parametrized circuit for dynamical maps in the next section.
}

@@

Finally, using the representation of Pauli channels in a tetrahedron as in
\eref{eq: conditions-tetrahedron}, we show in \fref{Fig3} the diamond
fidelity defined by \eref{eq:diamond-fid} for the channels analyzed.  We can
see that channels close to the completely depolarizing channel (that is close
to the center of the tetrahedron) have a high $f$, while those close to unitary
channels have much lower $f$. \revnote{So another way to see this is that the simulation through the proposed decomposition works only for depolarising channels, and fails otherwise. } 
\tbnote{La respuesta a esto puede incluir lo siguiente: 
It works better for depolarizing channels, yes, but still has considerably big zone with high fidelity.}
 This is reasonable because quantum computers are
prone to errors that depolarize qubits, which isn't very problematic when
trying to simulate depolarization but it is when simulating unitary processes.
Moreover, the algorithm of \fref{Fig2} is not optimal for
unitary channels \revnote{why?} (that is, the channels corresponding to the vertices of the
tetrahedron).  These straightforward channels could be accomplished more
efficiently by simply applying the corresponding Pauli operation directly. \revnote{I wholeheartedly agree with this statement, and I would go so far as to claim that this is true in general, even at the center of the tethraedron.}
\tbnote{Este comentario se conecta con lo del 
primer comentario, que no sé bien cómo contestar.}
Nevertheless, due to its general design to accommodate any Pauli channel, the
algorithm employs numerous quantum gates even in such scenarios. \revnote{but this is a severe disadvantage, that begs the question: what is the advantage?}
\tbnote{As I see it, an advantage is that only one circuit arrengment is needed for any channel. We don't have to change
the circuit to implement different channels, only need to change parameters.
This allows us to consider parametrized circuits and then explore what happens when
we constrain to only one parametrized operation.}\\
\tbnote{Se podría entonces cambiar la ultima oración del texto por la siguiente para que quede más claro:}
{\color{green} This disadvantage comes from the fact
that the circuit is  fully general and applicable to any Pauli channel, but that means that sometimes
it is not the most straightforward algorithm to simulate a Pauli channel.
However, the main advantage is that if we want 
to simulate many Pauli channels (for example,
for simulating a Pauli dynamical map as we will see later),
we only have to change a couple of angles in the circuit and
not completely reconstruct it. 
And as we will see, sometimes only changing
one angle in the circuit will be enough.}\\
$\;$\\

\tbnote{Sección que agregué:}\\

@@

{\color{green}
Finally, we move to the main goal of this article, which is 
simulating Pauli dynamical maps.
This is pretty much already solved, since
just as Pauli channels, Pauli dynamical maps can be implemented using the circuit
of \fref{Fig1}.} However, there is one difference: 
the state to be created on the ancilla qubits now 
depends on a parameter $p$, and it is represented by the expression:
\begin{eqnarray}
\label{eq: parametrized state}
\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle.
\end{eqnarray}
Thus, we temporarily shift our focus from Pauli
channels and dynamical maps to the general problem of 
creating a circuit to generate a curve of
states like the one described in \eref{eq: parametrized state}.

@@

In this work, we found a quantum algorithm for 
simulating Pauli channels in $N$-qubit systems and
generalized it to Pauli dynamical maps
by using parametrized quantum circuits \revnote{imprecise} \tbnote{No sé exactamente qué es imprecise}.
Furthermore, we implemented single-qubit Pauli channels
on one of IBM's quantum computers
and obtained their fidelities. 
Finally, when working with Pauli dynamical maps,
we searched for a way of simplifying the parametrized circuit \revnote{This reasoning I miss, simplifying for achieving what goal? }
by requiring that only one single-qubit rotation depends on the parameter.
In theorem \ref{theorem2} we found the general mathematical conditions for 
this, applicable to any parametrized circuit.

Therefore, this work presents yet another example of the current
exploration into simulating open quantum
systems in quantum computers,
and we observe the big effect that the error of quantum computers have
on these simulations. \revnote{There is no quantification of this, it´s not even the focus of the paper}
On the other hand, the result
of theorem \ref{theorem2}
shows what can be done with the condition of using only one
parametrized rotation and
can be applied to any quantum algorithm that requires parametrized circuits,
such as those used for quantum machine learning~\cite{Benedetti}.
